%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experiences}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}
\cventry
{Long Term Intern} % Job title
{Denizbank} % Organization
{Denizbank Headquarters, Istanbul} % Location
{Feb. 2020 - Aug. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Selected as one of the 25 senior students for ``Deniz'in İncileri'' Internship Programme. Currectly working for the team specialized on Denizbank's growing mobile wallet application, fastPay.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Mobile Application Developer} % Job title
{Hummingdrone Co.} % Organization
{İTÜ Teknokent, Istanbul} % Location
{Jul. 2019 - Nov. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked as a mobile application developer. I've used React Native and Expo to create cross-platform applications.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Part-Time Teacher} % Job title
{Şişli Terakki Foundation Schools} % Organization
{Istanbul, Turkey} % Location
{Feb. 2019 - Feb. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked as a teacher for the Maths and Coding Club, gave coding classes for high school students once a week.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Student Assistant} % Job title
{Çırak Atölye} % Organization
{Istanbul, Turkey} % Location
{Nov. 2018 - Apr. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Organized basic programming lectures for high school students, using Racket to create 2D games.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Working Student} % Job title
{Istanbul Bilgi University} % Organization
{Istanbul, Turkey} % Location
{Nov. 2018 - May 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked for Computer Engineering Department, assisted professor's with their tasks.}
\end{cvitems}
}

\end{cventries}