%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Activities,Courses, Senior Design Project}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}


\cventry
{Frontend Developer} % Role
{Senior Design Project - Shelty} % Event
{Istanbul, Turkey} % Location
{Sep. 2019 - PRESENT} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {As Team Shelty, me and my two other friends, realized that there's no application about pet adoption in Turkey. So we decided to develop one using React Native, with the help of our framework, we created our application for both Android and iOS platforms. Now even though we completed our course successfully, we are still working on new features to make it a better application for users and pets.}
\end{cvitems}
}

%----------------------------------------------------------------------------------------

\cventry
{Head of Istanbul Bilgi University Free Software Club} % Role
{Free Software Club} % Event
{Istanbul, Turkey} % Location
{Sep. 2018 - PRESENT} % Date(s)
{ % Description(s)
}

%------------------------------------------------

\cventry
{Participant} % Role
{Re-Coded Android Bootcamp} % Event
{Istanbul, Turkey} % Location
{12 Mar. 2018- Jul. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {I'm one of the 34 people who's been selected to this bootcamp. We developed Android apps using Udacity's Google certificated Nanodegree materials. We covered: User Interface, User Input, Multi-Screen Apps, Fragments, Networking using JSON, SQLite Database for Android programming.}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Professional Archer} % Role
{United Nature Sports Club Archer} % Event
{Istanbul, Turkey} % Location
{Dec. 2015- PRESENT} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Participating in national competitions since 2015}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Istanbul Bilgi University Archery Club Administration Member} % Role
{Istanbul Bilgi University Archery Club} % Event
{Istanbul, Turkey} % Location
{Dec. 2015- PRESENT} % Date(s)
{}% Description(s)



%------------------------------------------------

\cventry
{} % Role
{Courses Completed on Udemy} % Event
{Istanbul, Turkey} % Location
{2016 - PRESENT} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {LateX for Professional Publications by Toni Farley}
\item {React Native - The Practical Guide by Maximilian Schwarzmüller}
\item {Git Complete: The Definitive, step-by-step Guide to Git by Jason Taylor}
\item {Fundamentals of Computer Hacking by infySEC Global}
\item {Linux BASH Shell Terminal Command Basics by JP Courses}
\item {The Complete Cyber Security Course by Nathan House}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}